The Accuracy of KNN, SVM, Bayes classifier, SVDD, neural network with DBSCAN, k-means, NN-chain for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types

### 2023-05-31 final/paper/main.tex
update Bayes

\title{The Accuracy of KNN, SVM, SVDD, neural network and DBSCAN, k-means for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types}

@@

\section*{Abstract}
Nowadays, using machine to give an early diagnosis of a cancer type is widely studied. 
In this paper, based on the gene-expression dataset on Synapse.org, we compare the performance of machine 
learning techniques, including data preprocessing, e.g., Principal components analysis (PCA), Autoencoder 
(AE), classification, e.g., k-nearest neighbors (KNN), support vector machine (SVM), neural network (NN), 
and clustering for dealing with unknown types, e.g., k-means, density-based spatial clustering of 
applications with noise (DBSCAN).

@@

@@

@@

  \begin{table*}[tb]
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques. (Arrhythmia dataset)}}
      \vspace{-\baselineskip}
    \resizebox{\textwidth}{!}{
      \begin{tabular}{@{}lcccccccccccc@{}}\toprule
        Method                    & \multicolumn{2}{c}{Raw}                     & \multicolumn{2}{c}{Normalized}   & \multicolumn{2}{c}{PCA-32}        & \multicolumn{2}{c}{PCA-32 Normalized} & \multicolumn{2}{c}{AE-32}        & \multicolumn{2}{c}{AE-32 Normalized} \\ 
        \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}
                                  & Search (s) & acc                            & Search (s) & acc                 & Search (s) & acc                  & Search (s) & acc                      & Search (s) & acc                  & Search (s) & acc            \\ \midrule
      KNN-Brute-Force + DBSCAN    & $0.0285$   & $47.4684 \pm 0$                & $0.0254$   & $46.8354 \pm 0$     & $0.0070$   & $38.6076 \pm 0$      & $0.0071$   & $42.4051\pm 0$           & $0.0071$   & $\bf{37.9747} \pm 0$ & $0.0071$   & $\bf{44.3038} \pm 0$\\
      SVM (linear) + DBSCAN       & $1.7269$   & $25.9494 \pm 0$                & $8.9285$   & $35.4430 \pm 0$     & $0.2186$   & $32.2785 \pm 0$      & $0.8162$   & $29.7468 \pm 0$          & $0.2169$   & $31.6456 \pm 0$      & $0.1552$   & $27.8481 \pm 0$\\
      SVM (polynomial) + DBSCAN   & $0.9993$   & $25.9494 \pm 0$                & $1.6100$   & $25.3165 \pm 0$     & $0.1997$   & $\z{1.2658} \pm 0$   & $0.4577$   & $33.5443 \pm 0$          & $0.2402$   & $30.3797 \pm 0$      & $0.4924$   & $30.2785 \pm 0$\\
      SVM (RBF) + DBSCAN          & $0.9915$   & $25.9494 \pm 0$                & $1.4681$   & $22.7848 \pm 0$     & $1.4328$   & $\z{0.6329} \pm 0$   & $11.9417$  & $30.3797 \pm 0$          & $13.5147$  & $22.1519 \pm 0$      & $24.7346$  & $34.1772 \pm 0$\\
      SVM (sigmoid) + DBSCAN      & $3.5272$   & $28.4810 \pm 0$                & $6.4731$   & $20.2532 \pm 0$     & $1.5779$   & $30.3797 \pm 0$      & $0.9797$   & $36.0759 \pm 0$          & $0.5284$   & $22.1519 \pm 0$      & $0.8430$   & $24.6835 \pm 0$\\
      KNN-Brute-Force + kmeans    & $0.0236$   & $\bf{53.1646} \pm 0$           & $0.0343$   & $\bf{50.6329} \pm 0$& $0.0068$   & $\bf{43.0380} \pm 0$ & $0.0069$   & $\bf{43.0380} \pm 0$     & $0.0069$   & $36.0759 \pm 0$      & $0.0080$   & $41.7722 \pm 0$\\
      SVM (linear) + kmeans       & $1.7719$   & $25.3165 \pm 0$                & $37.9747$  & $37.9747 \pm 0$     & $0.2317$   & $25.3165 \pm 0$      & $0.8932$   & $27.8481 \pm 0$          & $0.2331$   & $24.0506 \pm 0$      & $0.1596$   & $20.2532 \pm 0$\\
      SVM (polynomial) + kmeans   & $1.0456$   & $25.3165 \pm 0$                & $1.4942$   & $26.5823 \pm 0$     & $0.2326$   & $14.5570 \pm 0$      & $0.4094$   & $28.4810 \pm 0$          & $0.2033$   & $24.0506 \pm 0$      & $0.4884$   & $25.3165 \pm 0$\\
      SVM (RBF) + kmeans          & $34.5382$  & $\z{8.8608} \pm 0$             & $43.0936$  & $29.7468 \pm 0$     & $110.589$  & $\z{0.6329} \pm 0$   & $112.945$  & $\z{1.2658} \pm 0$       & $38.7497$  & $22.7848 \pm 0$      & $14.1561$  & $27.2152 \pm 0$\\
      SVM (sigmoid) + kmeans      & $4.0277$   & $22.6582 \pm 0$                & $8.0918$   & $17.7848 \pm 0$     & $0.7529$   & $25.3165 \pm 0$      & $0.7967$   & $12.0253 \pm 0$          & $0.6921$   & $17.7215 \pm 0$      & $0.4013$   & $28.4810 \pm 0$\\     
      \bottomrule
      \end{tabular}
    }
    \label{table:Arrhythmia_result}
      \vspace{-\baselineskip}
  \end{table*}

  \begin{table*}[tb]
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques. (gene expression cancer RNA-Seq dataset)}}
      \vspace{-\baselineskip}
    \resizebox{\textwidth}{!}{
      \begin{tabular}{@{}lcccccccccccc@{}}\toprule
        Method                  & \multicolumn{2}{c}{Raw}        & \multicolumn{2}{c}{Normalized}     & \multicolumn{2}{c}{PCA-30}                & \multicolumn{2}{c}{PCA-30 Normalized} & \multicolumn{2}{c}{AE-30}         & \multicolumn{2}{c}{AE-30 Normalized} \\ 
        \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}
                                & Search (s) & acc               & Search (s) & acc                   & Search (s) & acc                          & Search (s) & acc                      & Search (s) & acc                  & Search (s) & acc            \\ \midrule
      KNN-Brute-Force + DBSCAN  & $14.5101$  & $59.0361 \pm 0$   & $10.3013$  & $\bf{66.5663} \pm 0$  & $0.0224$   & $94.5783 \pm 0$              & $0.0237$   & $78.3133 \pm 0$          & $0.0258$   & $\bf{64.4578} \pm 0$ & $0.0235$   & $59.3373 \pm 0$\\
      SVM (linear) + DBSCAN     & $124.593$  & $61.7470 \pm 0$   & $610.6730$ & $\z{9.9398} \pm 0$    & $0.6466$   & $\z{9.9398} \pm 0$           & $0.1193$   & $10.5422 \pm 0$          & $0.1407$   & $63.2530 \pm 0$      & $0.1122$   & $13.5542 \pm 0$\\
      SVM (polynomial) + DBSCAN & $81.6495$  & $61.7470 \pm 0$   & $86.6406$  & $\z{1.2048} \pm 0$    & $0.2585$   & $64.4578 \pm 0$              & $0.3012$   & $61.1446 \pm 0$          & $0.2013$   & $63.2530 \pm 0$      & $0.2056$   & $50.3012 \pm 0$\\
      SVM (RBF) + DBSCAN        & $X$        & $\text{not converge}$ & $X$    & $\text{not converge}$ & $12.5077$  & $\z{9.9398} \pm 0$           & $3.8838$   & $63.2530 \pm 0$          & $5.0461$   & $40.3614 \pm 0$      & $11.4194$  & $49.6988 \pm 0$\\
      SVM (sigmoid) + DBSCAN    & $X$        & $\text{not converge}$ & $X$    & $\text{not converge}$ & $0.6372$   & $71.6867 \pm 0$              & $0.8222$   & $65.9639 \pm 0$          & $0.6236$   & $44.2771 \pm 0$      & $0.2273$   & $38.2530 \pm 0$\\
      KNN-Brute-Force + kmeans  & $22.754$   & $\bf{74.0964} \pm 0$& $6.36577$& $53.6145 \pm 0$       & $0.0212$   & $\bf{94.8795} \pm 0$         & $0.0214$   & $\bf{84.9398} \pm 0$     & $0.0214$   & $42.1687 \pm 0$      & $0.0220$   & $\bf{65.9639} \pm 0$\\
      SVM (linear) + kmeans     & $136.408$  & $61.7470 \pm 0$   & $664.2860$ & $\z{9.9398} \pm 0$    & $0.5914$   & $\z{9.9398} \pm 0$           & $0.1077$   & $10.5422 \pm 0$          & $0.1274$   & $63.2530 \pm 0$      & $0.1084$   & $13.2530 \pm 0$\\
      SVM (polynomial) + kmeans & $81.4276$  & $61.7470 \pm 0$   & $81.1669$  & $63.8554 \pm 0$       & $0.2003$   & $64.4578 \pm 0$              & $0.2167$   & $25.3012 \pm 0$          & $0.1780$   & $63.2530 \pm 0$      & $0.1930$   & $50.3012 \pm 0$\\
      SVM (RBF) + kmeans        & $1772.32$  & $\z{9.9398} \pm 0$& $1800.6$   & $\z{9.9398} \pm 0$    & $1.3625$   & $\z{9.9398} \pm 0$           & $1.3848$   & $\z{9.9398} \pm 0$       & $11.1729$  & $39.7590 \pm 0$      & $4.7882$   & $28.6145 \pm 0$\\
      SVM (sigmoid) + kmeans    & $190.866$  & $26.5060 \pm 0$   & $81.7487$  & $63.8554 \pm 0$       & $0.8287$   & $65.9639 \pm 0$              & $0.4269$   & $65.9639 \pm 0$          & $0.9908$   & $28.9157 \pm 0$      & $0.2360$   & $39.4578 \pm 0$\\
      \bottomrule
      \end{tabular}
    }
    \label{table:gene_expression_result}
      \vspace{-\baselineskip}
  \end{table*}

\section{Conclusion}
In this study, we present a framework of algorithm to deal with the dataset containing 
out-of-knowledge data. And with in this algorithm, multiple major machine learning 
techniques are used, e.g., for preprocess, PCA, AE, normalization; for classification, 
KNN, SVM, SVDD, NN, as for clustering, DBSCAN, k-means, NN-chain. Among the various 
combinations, PCA + KNN + k-means performs outstanding in gene expression cancer RNA-Seq 
dataset, and raw data + KNN + k-means performs the best in arrhythmia dataset. Accidently, 
SVM performs bad in these two dataset. The main cause is the defect of the multi-classification 
SVMs design, which make some SVMs hard to separate the target types. However, by customize 
the kernel for each SVM, the problem may ease. In the same time, the increasing number of 
parameters can be fine-tuned by metaheuristic algorithms, e.g., simulated annealing, genetic 
algorithm, etc. We will develope a refinement design on multi-classification SVMs, to enhance 
the accuracy on these datasets.

\section{Contribution}
\begin{itemize}
  \item Hsieh Cheng-Han: KNN, SVM, DBSCAN, paper, ppt
  \item Hsu Ting-Hao: 
  \item Sun Shih-Yu: SVM, k-means, paper
  \item Lu Che-Yuan: 
  \item Huang Chia-Yen: 
\end{itemize}

>>>>

\title{The Accuracy of KNN, SVM, Bayes classifier, SVDD, neural network with DBSCAN, k-means, NN-chain for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types}

@@

\section*{Abstract}
Nowadays, using machine to give an early diagnosis of a cancer type is widely studied. 
In this paper, based on the gene-expression dataset on Synapse.org, we compare the performance of machine 
learning techniques, including data preprocessing, e.g., Principal components analysis (PCA), Autoencoder 
(AE), classification, e.g., k-nearest neighbors (KNN), support vector machine (SVM), neural network (NN), 
Support Vector Data Description (SVDD), naive Bayes classifier; 
and clustering for dealing with unknown types, e.g., k-means, density-based spatial clustering of 
applications with noise (DBSCAN) and nearest-neighbor chain (NN-chain).

@@

\bf{naive Bayes classifier}: \rm{naive Bayes classifier} as its name suggest, is a machine learning method base on Bayesian 
theorem, this model will statistic each data and find all conditional probability of each event occurring if each outcome holds. 
And finally when it is asked to predict the result, the model will evaluate the data which requist provide and find the most 
likely outcome according to the conditional probability it just recorded.

@@

  As for Naive Bayes classifier, first assume there are $N$ known types. Denotes the $N$ Bayes classifiers recognizing each 
  type of known types as $B_1, B_2, ..., B_N$. For each test data, let $B_1$ determine whether it belongs to type 1, if 
  it does, mark it as type 1 and try classifying next test data, otherwise, $B_2$ will determine whether it belongs to type 2 
  or not, and so on. If all Bayes classifiers results false, namely, the data doesn't belong to any known types, marks it 
  as unknown type.

@@

  \begin{table*}[tb]
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques. (Arrhythmia dataset)}}
      \vspace{-\baselineskip}
    \resizebox{\textwidth}{!}{
      \begin{tabular}{@{}lcccccccccccc@{}}\toprule
        Method                    & \multicolumn{2}{c}{Raw}                     & \multicolumn{2}{c}{Normalized}   & \multicolumn{2}{c}{PCA-32}        & \multicolumn{2}{c}{PCA-32 Normalized} & \multicolumn{2}{c}{AE-32}        & \multicolumn{2}{c}{AE-32 Normalized} \\ 
        \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}
                                  & Search (s) & acc                            & Search (s) & acc                 & Search (s) & acc                  & Search (s) & acc                      & Search (s) & acc                  & Search (s) & acc            \\ \midrule
      KNN-Brute-Force + DBSCAN    & $0.0285$   & $47.4684 \pm 0$                & $0.0254$   & $46.8354 \pm 0$     & $0.0070$   & $38.6076 \pm 0$      & $0.0071$   & $42.4051\pm 0$           & $0.0071$   & $\bf{37.9747} \pm 0$ & $0.0071$   & $\bf{44.3038} \pm 0$\\
      SVM (linear) + DBSCAN       & $1.7269$   & $25.9494 \pm 0$                & $8.9285$   & $35.4430 \pm 0$     & $0.2186$   & $32.2785 \pm 0$      & $0.8162$   & $29.7468 \pm 0$          & $0.2169$   & $31.6456 \pm 0$      & $0.1552$   & $27.8481 \pm 0$\\
      SVM (polynomial) + DBSCAN   & $0.9993$   & $25.9494 \pm 0$                & $1.6100$   & $25.3165 \pm 0$     & $0.1997$   & $\z{1.2658} \pm 0$   & $0.4577$   & $33.5443 \pm 0$          & $0.2402$   & $30.3797 \pm 0$      & $0.4924$   & $30.2785 \pm 0$\\
      SVM (RBF) + DBSCAN          & $0.9915$   & $25.9494 \pm 0$                & $1.4681$   & $22.7848 \pm 0$     & $1.4328$   & $\z{0.6329} \pm 0$   & $11.9417$  & $30.3797 \pm 0$          & $13.5147$  & $22.1519 \pm 0$      & $24.7346$  & $34.1772 \pm 0$\\
      SVM (sigmoid) + DBSCAN      & $3.5272$   & $28.4810 \pm 0$                & $6.4731$   & $20.2532 \pm 0$     & $1.5779$   & $30.3797 \pm 0$      & $0.9797$   & $36.0759 \pm 0$          & $0.5284$   & $22.1519 \pm 0$      & $0.8430$   & $24.6835 \pm 0$\\
      KNN-Brute-Force + kmeans    & $0.0236$   & $\bf{53.1646} \pm 0$           & $0.0343$   & $\bf{50.6329} \pm 0$& $0.0068$   & $\bf{43.0380} \pm 0$ & $0.0069$   & $\bf{43.0380} \pm 0$     & $0.0069$   & $36.0759 \pm 0$      & $0.0080$   & $41.7722 \pm 0$\\
      SVM (linear) + kmeans       & $1.7719$   & $25.3165 \pm 0$                & $37.9747$  & $37.9747 \pm 0$     & $0.2317$   & $25.3165 \pm 0$      & $0.8932$   & $27.8481 \pm 0$          & $0.2331$   & $24.0506 \pm 0$      & $0.1596$   & $20.2532 \pm 0$\\
      SVM (polynomial) + kmeans   & $1.0456$   & $25.3165 \pm 0$                & $1.4942$   & $26.5823 \pm 0$     & $0.2326$   & $14.5570 \pm 0$      & $0.4094$   & $28.4810 \pm 0$          & $0.2033$   & $24.0506 \pm 0$      & $0.4884$   & $25.3165 \pm 0$\\
      SVM (RBF) + kmeans          & $34.5382$  & $\z{8.8608} \pm 0$             & $43.0936$  & $29.7468 \pm 0$     & $110.589$  & $\z{0.6329} \pm 0$   & $112.945$  & $\z{1.2658} \pm 0$       & $38.7497$  & $22.7848 \pm 0$      & $14.1561$  & $27.2152 \pm 0$\\
      SVM (sigmoid) + kmeans      & $4.0277$   & $22.6582 \pm 0$                & $8.0918$   & $17.7848 \pm 0$     & $0.7529$   & $25.3165 \pm 0$      & $0.7967$   & $12.0253 \pm 0$          & $0.6921$   & $17.7215 \pm 0$      & $0.4013$   & $28.4810 \pm 0$\\
      Bayes-GA + kmeans           & $X$        & $X$                            & $X$        & $X$                 & $0.0294$   & $14.5570 \pm 0$      & $X$        & $X$                      & $0.0297$   & $15.8228 \pm 0$      & $X$        & $X$            \\
      \bottomrule
      \end{tabular}
    }
    \label{table:Arrhythmia_result}
      \vspace{-\baselineskip}
  \end{table*}

  \begin{table*}[tb]
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques. (gene expression cancer RNA-Seq dataset)}}
      \vspace{-\baselineskip}
    \resizebox{\textwidth}{!}{
      \begin{tabular}{@{}lcccccccccccc@{}}\toprule
        Method                  & \multicolumn{2}{c}{Raw}        & \multicolumn{2}{c}{Normalized}     & \multicolumn{2}{c}{PCA-30}                & \multicolumn{2}{c}{PCA-30 Normalized} & \multicolumn{2}{c}{AE-30}         & \multicolumn{2}{c}{AE-30 Normalized} \\ 
        \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}
                                & Search (s) & acc               & Search (s) & acc                   & Search (s) & acc                          & Search (s) & acc                      & Search (s) & acc                  & Search (s) & acc            \\ \midrule
      KNN-Brute-Force + DBSCAN  & $14.5101$  & $59.0361 \pm 0$   & $10.3013$  & $\bf{66.5663} \pm 0$  & $0.0224$   & $94.5783 \pm 0$              & $0.0237$   & $78.3133 \pm 0$          & $0.0258$   & $\bf{64.4578} \pm 0$ & $0.0235$   & $59.3373 \pm 0$\\
      SVM (linear) + DBSCAN     & $124.593$  & $61.7470 \pm 0$   & $610.6730$ & $\z{9.9398} \pm 0$    & $0.6466$   & $\z{9.9398} \pm 0$           & $0.1193$   & $10.5422 \pm 0$          & $0.1407$   & $63.2530 \pm 0$      & $0.1122$   & $13.5542 \pm 0$\\
      SVM (polynomial) + DBSCAN & $81.6495$  & $61.7470 \pm 0$   & $86.6406$  & $\z{1.2048} \pm 0$    & $0.2585$   & $64.4578 \pm 0$              & $0.3012$   & $61.1446 \pm 0$          & $0.2013$   & $63.2530 \pm 0$      & $0.2056$   & $50.3012 \pm 0$\\
      SVM (RBF) + DBSCAN        & $X$        & $\text{not converge}$ & $X$    & $\text{not converge}$ & $12.5077$  & $\z{9.9398} \pm 0$           & $3.8838$   & $63.2530 \pm 0$          & $5.0461$   & $40.3614 \pm 0$      & $11.4194$  & $49.6988 \pm 0$\\
      SVM (sigmoid) + DBSCAN    & $X$        & $\text{not converge}$ & $X$    & $\text{not converge}$ & $0.6372$   & $71.6867 \pm 0$              & $0.8222$   & $65.9639 \pm 0$          & $0.6236$   & $44.2771 \pm 0$      & $0.2273$   & $38.2530 \pm 0$\\
      KNN-Brute-Force + kmeans  & $22.754$   & $\bf{74.0964} \pm 0$& $6.36577$& $53.6145 \pm 0$       & $0.0212$   & $\bf{94.8795} \pm 0$         & $0.0214$   & $\bf{84.9398} \pm 0$     & $0.0214$   & $42.1687 \pm 0$      & $0.0220$   & $\bf{65.9639} \pm 0$\\
      SVM (linear) + kmeans     & $136.408$  & $61.7470 \pm 0$   & $664.2860$ & $\z{9.9398} \pm 0$    & $0.5914$   & $\z{9.9398} \pm 0$           & $0.1077$   & $10.5422 \pm 0$          & $0.1274$   & $63.2530 \pm 0$      & $0.1084$   & $13.2530 \pm 0$\\
      SVM (polynomial) + kmeans & $81.4276$  & $61.7470 \pm 0$   & $81.1669$  & $63.8554 \pm 0$       & $0.2003$   & $64.4578 \pm 0$              & $0.2167$   & $25.3012 \pm 0$          & $0.1780$   & $63.2530 \pm 0$      & $0.1930$   & $50.3012 \pm 0$\\
      SVM (RBF) + kmeans        & $1772.32$  & $\z{9.9398} \pm 0$& $1800.6$   & $\z{9.9398} \pm 0$    & $1.3625$   & $\z{9.9398} \pm 0$           & $1.3848$   & $\z{9.9398} \pm 0$       & $11.1729$  & $39.7590 \pm 0$      & $4.7882$   & $28.6145 \pm 0$\\
      SVM (sigmoid) + kmeans    & $190.866$  & $26.5060 \pm 0$   & $81.7487$  & $63.8554 \pm 0$       & $0.8287$   & $65.9639 \pm 0$              & $0.4269$   & $65.9639 \pm 0$          & $0.9908$   & $28.9157 \pm 0$      & $0.2360$   & $39.4578 \pm 0$\\
      Bayes-GA + kmeans         & $X$        & $X$               & $X$        & $X$                   & $X$        & $X$                          & $X$        & $X$                      & $0.0338$   & $27.7946 \pm 0$      & $X$        & $X$            \\
      \bottomrule
      \end{tabular}
    }
    \label{table:gene_expression_result}
      \vspace{-\baselineskip}
  \end{table*}

\section{Conclusion}
In this study, we present a framework of algorithm to deal with the dataset containing 
out-of-knowledge data. And with in this algorithm, multiple major machine learning 
techniques are used, e.g., for preprocess, PCA, AE, normalization; for classification, 
KNN, SVM, SVDD, NN, Bayes classifier, as for clustering, DBSCAN, k-means, NN-chain. Among the various 
combinations, PCA + KNN + k-means performs outstanding in gene expression cancer RNA-Seq 
dataset, and raw data + KNN + k-means performs the best in arrhythmia dataset. Accidently, 
SVM performs bad in these two dataset. The main cause is the defect of the multi-classification 
SVMs design, which make some SVMs hard to separate the target types. However, by customize 
the kernel for each SVM, the problem may ease. In the same time, the increasing number of 
parameters can be fine-tuned by metaheuristic algorithms, e.g., simulated annealing, genetic 
algorithm, etc. We will develope a refinement design on multi-classification SVMs, to enhance 
the accuracy on these datasets.

\section{Contribution}
\begin{itemize}
  \item Hsieh Cheng-Han: KNN, SVM, DBSCAN, paper, ppt
  \item Hsu Ting-Hao: 
  \item Sun Shih-Yu: SVM, k-means, paper
  \item Lu Che-Yuan: 
  \item Huang Chia-Yen: naive Bayes classifier, paper, poster
\end{itemize}
